---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = TRUE, cache = FALSE)
library(here)
# here::here()
knitr::opts_knit$set(root.dir = here::here())
```

```{r load_libs_sources, message=FALSE, warning=FALSE, cache=FALSE, echo=FALSE}
source('./R/utils_av.R')
```

```{r new_functions}

seas_yr_growth <- function(data_ts, freq = 4 , is_log = TRUE, 
                           do_just_log = FALSE) {
  
  seas_gr <- tsibble::as_tsibble(data_ts)
  
  if (is_log) {
    seas_gr  <- seas_gr %>% 
    mutate(difflog_gr =  100 * difference(value, lag = freq))
    
    year_gr <- seas_gr %>% index_by(year_index = year(index)) %>%
      summarise(y_logdiff = mean(difflog_gr, na.rm = TRUE)) 
    
    if (freq == 12) {
      quarter_gr <- seas_gr %>% index_by(quarter_index = yearquarter(index)) %>%
      summarise(q_logdiff = mean(difflog_gr, na.rm = TRUE)) 
    }
    
      if (! do_just_log) {
        seas_gr  <-seas_gr  %>% 
          mutate(gr = 100 * difference(exp(value), lag = freq) / 
                 dplyr::lag(exp(value), n = freq))
        
        year_gr <- seas_gr %>% index_by(year_index = year(index)) %>%
          summarise(y_logdiff = mean(difflog_gr, na.rm = TRUE),
                    y_ave_gr = mean(gr, na.rm = TRUE),
                    y_rgdp = sum(exp(value), na.rm = TRUE))  %>%
          mutate(y_tot_gr = 100*difference(y_rgdp)/lag(y_rgdp)) 
        
        if (freq == 12) {
          quarter_gr <- seas_gr %>% index_by(quarter_index = yearquarter(index)) %>%
          summarise(q_logdiff = mean(difflog_gr, na.rm = TRUE),
                    q_ave_gr = mean(gr, na.rm = TRUE),
                    q_rgdp = sum(exp(value), na.rm = TRUE))  %>%
          mutate(q_tot_gr = 100*difference(q_rgdp, lag = 4)/lag(q_rgdp, n = 4))
          
        }
      }
    
  } else {
    seas_gr  <-seas_gr  %>% 
          mutate(gr = 100 * difference(value, lag = freq) / 
                 dplyr::lag(value, n = freq))
    
    year_gr <- seas_gr %>% index_by(year_index = year(index)) %>% 
      summarise(y_ave_gr = mean(gr, na.rm = TRUE),
                y_rgdp = sum(value)) %>%
      mutate(y_tot_gr = 100*difference(y_rgdp)/lag(y_rgdp))
    
    if (freq == 12) {
      quarter_gr <- seas_gr %>% index_by(quarter_index = yearquarter(index)) %>% 
      summarise(q_ave_gr = mean(gr, na.rm = TRUE),
                q_rgdp = sum(value)) %>%
      mutate(q_tot_gr = 100*difference(q_rgdp, lag = 4)/lag(q_rgdp, n = 4))
    }
    
  }

  
  if (freq == 4) {
    return(list(seasonal_growth = seas_gr, year_growth = year_gr))
  }
  
  if (freq == 12) {
    return(list(seasonal_growth = seas_gr, year_growth = year_gr,
                quarter_growth = quarter_gr))
  }
  
  

}

print_growths <- function(seas_and_yr_gr) {
  seas_gr <- seas_and_yr_gr[["seasonal_growth"]]
  year_gr <- seas_and_yr_gr[["year_growth"]]
  quarter_gr <- seas_and_yr_gr[["quarter_growth"]]

  seas <- knitr::kable(tail(as_tibble(seas_gr) %>% select(-value), n = 8), 
             digits = 1, align = 'lcc')

  yr <- knitr::kable(tail(as_tibble(year_gr) %>% select(-y_rgdp), n = 5),
               digits = 1, align = 'lccc')  
  
  if (is.null(quarter_gr)) {
    
    walk(list(seas, yr), print)
    
  } else {
    
    qtr <- knitr::kable(tail(as_tibble(quarter_gr) %>% select(-q_rgdp), n = 5),
               digits = 1, align = 'lccc') 
    
    walk(list(seas, yr, qtr), print)
    
  }
  
}

```



## Initial data


```{r preferences_and_load_data, warning=FALSE}
arima_res_suffix <- "_min"
arima_rds_path = "data/sarimax_objects_"
country_name <- "Bolivia_activ"
# data_path <- "./data/excel/Chile.xlsx"
data_path <- paste0("./data/excel/", country_name, ".xlsx")
external_data_path <- "./data/external/external_us.xlsx"
is_log_log <- TRUE

all_arima_data <- ts_data_for_arima(data_path = data_path, 
                                    external_data_path = external_data_path,
                                    all_logs = is_log_log)

this_rgdp_ts <- all_arima_data[["rgdp_ts"]]
this_rgdp_ts <- na.omit(this_rgdp_ts)

this_internal_monthly_ts <- all_arima_data[["monthly_ts"]]
this_external_monthly_ts <- all_arima_data[["external_monthly_ts"]]

internal_monthly_names <- colnames(this_internal_monthly_ts)
external_monthly_names <- colnames(this_external_monthly_ts)

```

Log transformation applied to all variables. Data obtained from the excel file `r print(data_path)` 

### Quarterly real GDP


```{r plot_level_rgdp}
autoplot(this_rgdp_ts) + 
  ggtitle(paste("Quarterly GDP")) 

```


```{r plot_yoy_gr_rgdp}

autoplot(make_yoy_ts(this_rgdp_ts, is_log = TRUE)) + 
  ggtitle(paste("YoY growth, Quarterly GDP")) 
```


```{r plot_level_e_i}
autoplot(this_internal_monthly_ts, series = "internal") + 
  autolayer(this_external_monthly_ts, series = "external")

ei_level_ts  <- ts.union(int = na.omit(this_internal_monthly_ts), 
                         ext = na.omit(this_external_monthly_ts))

tail_level <- tail(ei_level_ts, n = 12)

tail_level 
```

```{r plot_yoy_growth_e_i}
autoplot(make_yoy_ts(this_internal_monthly_ts, freq = 12, is_log = TRUE),
         series = "internal") + 
  autolayer(make_yoy_ts(this_external_monthly_ts, freq = 12, is_log = TRUE),
            series = "external") 


ei_yoy_gr_ts  <- ts.union(int = na.omit(
  make_yoy_ts(this_internal_monthly_ts, freq = 12, is_log = TRUE)), 
                         ext = na.omit(
  make_yoy_ts(this_external_monthly_ts, freq = 12, is_log = TRUE))
                           )

tail_yoy <- 100*tail(ei_yoy_gr_ts, n = 14)


  
tail_yoy

```


Data availability notes:

- Our key data, real GDP is available up to 2017 Q3
- The internal variable (monthly activity index) is available only up to May 2017. This is, partially covers 2017 Q2 but none of 2017 Q3.
- The external variable (monthly US activity index) is available up to February 2018, partially covering 2018 Q1.



### Quarterly versions of GDP and monthly data 

In terms of growth rates
```{r gr_data}

gr_q_y_rgdp <- seas_yr_growth(na.omit(this_rgdp_ts))
gr_m_y_q_internal <- seas_yr_growth(na.omit(this_internal_monthly_ts), 
                                    freq = 12)
gr_m_y_q_external <- seas_yr_growth(na.omit(this_external_monthly_ts),
                                    freq = 12)

q_r_growth <- gr_q_y_rgdp$seasonal_growth %>% 
  rename(quarter_index = index, rgdp_growth = gr) %>%
  select(quarter_index, rgdp_growth)
  
q_e_growth <- gr_m_y_q_internal$quarter_growth %>% 
  rename(dom_growth = q_ave_gr) %>% 
  select(quarter_index, dom_growth)

q_i_growth <- gr_m_y_q_external$quarter_growth %>% 
  rename(ext_growth = q_ave_gr) %>% 
  select(quarter_index, ext_growth)

q_rie_growth <- left_join(q_r_growth, q_i_growth, by = "quarter_index") %>% 
  left_join(q_e_growth, by = "quarter_index")


knitr::kable(tail(q_rie_growth, n = 8), digits = 1)


# print_growths(gr_q_y)
# walk(gr_q_y, ~ print(tail(.)))
# walk(gr_m_y_q_internal, ~ print(tail(.)))
# walk(gr_m_y_q_external, ~ print(tail(.)))


```



## Initial GDP specification and forecast


```{r rgpd_uncond_arimas_dm_force}
final_forecast_horizon <- c(2019, 12)
h_max <-  8 # last rgdp data is 2017 Q4
test_length <- h_max
number_of_cv = 8
train_span = 16
use_demetra <- TRUE

use_dm_force_constant <- TRUE

lambda_0_in_auto <- FALSE
mean_logical_in_auto <- TRUE
max_x_lag <- 2


if (use_demetra) {
  do_auto <- FALSE
  demetra_output <- get_demetra_params(data_path)
  demetra_output_external <- get_demetra_params(external_data_path)
  
  rgdp_order_list <- demetra_output[["rgdp_order_list"]][[1]]
  
  fit_arima_rgdp_list_dem <- fit_arimas(
    y_ts = this_rgdp_ts, order_list = demetra_output[["rgdp_order_list"]],
    this_arima_names = "rgdp")
  
  this_rgdp_arima <- fit_arima_rgdp_list_dem
  
  monthly_with_demetra_info <- names(demetra_output[["monthly_order_list"]])
  log_vec <- internal_monthly_names %in% monthly_with_demetra_info
  if (any(!log_vec)) {
    print("At least one of the variables in monthly does not have a DEMETRA line and will not be considered.")
    print("These variables are:")
    print(internal_monthly_names[!log_vec])
    internal_monthly_names <- internal_monthly_names[log_vec]
    this_internal_monthly_ts <- this_internal_monthly_ts[, internal_monthly_names]
  }
  
  
  if (use_dm_force_constant) {
    this_non_external <- "non_external_dm_s" 
    this_external <- "external_dm_s" 
    do_dm_strict <-  FALSE
  } else {
    this_non_external <- "non_external_dm_r" 
    this_external <- "external_dm_r" 
    do_dm_strict <-  TRUE
  }
} else {
  do_auto <- TRUE
  fit_arima_rgdp_list_auto <- fit_arimas(y_ts = this_rgdp_ts, auto = TRUE,  
                                         this_arima_names = "rgdp", 
                                         my_lambda = NULL,
                                         do_approximation = TRUE)
  this_rgdp_arima <- fit_arima_rgdp_list_auto
  
  gdp_order <- get_order_from_arima(this_rgdp_arima)[[1]]
  rgdp_order <-  gdp_order[c("p", "d", "q")]
  rgdp_seasonal <-  gdp_order[c("P", "D", "Q")]
  
  rgdp_order_list <- list(order = rgdp_order, seasonal = rgdp_seasonal,
                          mean_logical = mean_logical_in_auto,
                          log_logical = lambda_0_in_auto)
  
  do_dm_strict <-  TRUE
  this_non_external <- "non_external_auto_r" 
  this_external <- "external_auto_r"
  demetra_output <- NULL
  demetra_output_external <- NULL
}


rgdp_uncond_fc <- forecast(this_rgdp_arima[["rgdp"]], h = h_max)
rgdp_uncond_fc_mean <- rgdp_uncond_fc$mean

rgdp_and_uncond_fc_dm_f <- ts(data = c(rgdp_uncond_fc$x, 
                                  rgdp_uncond_fc$mean), 
                         frequency = 4,
                         start = start(this_rgdp_ts))

gr_q_y_rgdp_and_unc_fc_dm_f <- seas_yr_growth(na.omit(rgdp_and_uncond_fc_dm_f))

q_rfc_growth_dm_f <- gr_q_y_rgdp_and_unc_fc_dm_f$seasonal_growth %>% 
  rename(quarter_index = index, rgdp_growth_dm_f = gr) %>%
  select(quarter_index, rgdp_growth_dm_f)

print(this_rgdp_arima[["rgdp"]])

# pander::pander(this_rgdp_arima[["rgdp"]])
# 
# autoplot(rgdp_uncond_fc)
# 
# knitr::kable(tail(q_rfc_growth_dm_f, n = 11), digits = 1)


```



```{r rgpd_uncond_arimas_dm_not_force}
final_forecast_horizon <- c(2019, 12)
h_max <-  8 # last rgdp data is 2017 Q4
test_length <- h_max
number_of_cv = 8
train_span = 16
use_demetra <- TRUE

use_dm_force_constant <- FALSE

lambda_0_in_auto <- FALSE
mean_logical_in_auto <- TRUE
max_x_lag <- 2


if (use_demetra) {
  do_auto <- FALSE
  demetra_output <- get_demetra_params(data_path)
  demetra_output_external <- get_demetra_params(external_data_path)
  
  rgdp_order_list <- demetra_output[["rgdp_order_list"]][[1]]
  
  fit_arima_rgdp_list_dem <- fit_arimas(
    y_ts = this_rgdp_ts, order_list = demetra_output[["rgdp_order_list"]],
    this_arima_names = "rgdp")
  
  this_rgdp_arima <- fit_arima_rgdp_list_dem
  
  monthly_with_demetra_info <- names(demetra_output[["monthly_order_list"]])
  log_vec <- internal_monthly_names %in% monthly_with_demetra_info
  if (any(!log_vec)) {
    print("At least one of the variables in monthly does not have a DEMETRA line and will not be considered.")
    print("These variables are:")
    print(internal_monthly_names[!log_vec])
    internal_monthly_names <- internal_monthly_names[log_vec]
    this_internal_monthly_ts <- this_internal_monthly_ts[, internal_monthly_names]
  }
  
  
  if (use_dm_force_constant) {
    this_non_external <- "non_external_dm_s" 
    this_external <- "external_dm_s" 
    do_dm_strict <-  FALSE
  } else {
    this_non_external <- "non_external_dm_r" 
    this_external <- "external_dm_r" 
    do_dm_strict <-  TRUE
  }
} else {
  do_auto <- TRUE
  fit_arima_rgdp_list_auto <- fit_arimas(y_ts = this_rgdp_ts, auto = TRUE,  
                                         this_arima_names = "rgdp", 
                                         my_lambda = NULL,
                                         do_approximation = TRUE)
  this_rgdp_arima <- fit_arima_rgdp_list_auto
  
  gdp_order <- get_order_from_arima(this_rgdp_arima)[[1]]
  rgdp_order <-  gdp_order[c("p", "d", "q")]
  rgdp_seasonal <-  gdp_order[c("P", "D", "Q")]
  
  rgdp_order_list <- list(order = rgdp_order, seasonal = rgdp_seasonal,
                          mean_logical = mean_logical_in_auto,
                          log_logical = lambda_0_in_auto)
  
  do_dm_strict <-  TRUE
  this_non_external <- "non_external_auto_r" 
  this_external <- "external_auto_r"
  demetra_output <- NULL
  demetra_output_external <- NULL
}


rgdp_uncond_fc <- forecast(this_rgdp_arima[["rgdp"]], h = h_max)
rgdp_uncond_fc_mean <- rgdp_uncond_fc$mean

rgdp_and_uncond_fc_dm_nf <- ts(data = c(rgdp_uncond_fc$x, 
                                  rgdp_uncond_fc$mean), 
                         frequency = 4,
                         start = start(this_rgdp_ts))

gr_q_y_rgdp_and_unc_fc_dm_nf <- seas_yr_growth(na.omit(rgdp_and_uncond_fc_dm_nf))

q_rfc_growth_dm_nf <- gr_q_y_rgdp_and_unc_fc_dm_nf$seasonal_growth %>% 
  rename(quarter_index = index, rgdp_growth_dm_nf = gr) %>%
  select(quarter_index, rgdp_growth_dm_nf)

print(this_rgdp_arima[["rgdp"]])

# pander::pander(this_rgdp_arima[["rgdp"]])

# autoplot(rgdp_uncond_fc)
# 
# knitr::kable(tail(q_rfc_growth, n = 11), digits = 1)


```



```{r rgpd_uncond_arimas_auto}
final_forecast_horizon <- c(2019, 12)
h_max <-  8 # last rgdp data is 2017 Q4
test_length <- h_max
number_of_cv = 8
train_span = 16
use_demetra <- FALSE

use_dm_force_constant <- TRUE

lambda_0_in_auto <- FALSE
mean_logical_in_auto <- TRUE
max_x_lag <- 2


if (use_demetra) {
  do_auto <- FALSE
  demetra_output <- get_demetra_params(data_path)
  demetra_output_external <- get_demetra_params(external_data_path)
  
  rgdp_order_list <- demetra_output[["rgdp_order_list"]][[1]]
  
  fit_arima_rgdp_list_dem <- fit_arimas(
    y_ts = this_rgdp_ts, order_list = demetra_output[["rgdp_order_list"]],
    this_arima_names = "rgdp")
  
  this_rgdp_arima <- fit_arima_rgdp_list_dem
  
  monthly_with_demetra_info <- names(demetra_output[["monthly_order_list"]])
  log_vec <- internal_monthly_names %in% monthly_with_demetra_info
  if (any(!log_vec)) {
    print("At least one of the variables in monthly does not have a DEMETRA line and will not be considered.")
    print("These variables are:")
    print(internal_monthly_names[!log_vec])
    internal_monthly_names <- internal_monthly_names[log_vec]
    this_internal_monthly_ts <- this_internal_monthly_ts[, internal_monthly_names]
  }
  
  
  if (use_dm_force_constant) {
    this_non_external <- "non_external_dm_s" 
    this_external <- "external_dm_s" 
    do_dm_strict <-  FALSE
  } else {
    this_non_external <- "non_external_dm_r" 
    this_external <- "external_dm_r" 
    do_dm_strict <-  TRUE
  }
} else {
  do_auto <- TRUE
  fit_arima_rgdp_list_auto <- fit_arimas(y_ts = this_rgdp_ts, auto = TRUE,  
                                         this_arima_names = "rgdp", 
                                         my_lambda = NULL,
                                         do_approximation = TRUE)
  this_rgdp_arima <- fit_arima_rgdp_list_auto
  
  gdp_order <- get_order_from_arima(this_rgdp_arima)[[1]]
  rgdp_order <-  gdp_order[c("p", "d", "q")]
  rgdp_seasonal <-  gdp_order[c("P", "D", "Q")]
  
  rgdp_order_list <- list(order = rgdp_order, seasonal = rgdp_seasonal,
                          mean_logical = mean_logical_in_auto,
                          log_logical = lambda_0_in_auto)
  
  do_dm_strict <-  TRUE
  this_non_external <- "non_external_auto_r" 
  this_external <- "external_auto_r"
  demetra_output <- NULL
  demetra_output_external <- NULL
}


rgdp_uncond_fc <- forecast(this_rgdp_arima[["rgdp"]], h = h_max)
rgdp_uncond_fc_mean <- rgdp_uncond_fc$mean

rgdp_and_uncond_fc_auto <- ts(data = c(rgdp_uncond_fc$x, 
                                  rgdp_uncond_fc$mean), 
                         frequency = 4,
                         start = start(this_rgdp_ts))

gr_q_y_rgdp_and_unc_fc_auto <- seas_yr_growth(na.omit(rgdp_and_uncond_fc_auto))

q_rfc_growth_auto <- gr_q_y_rgdp_and_unc_fc_auto$seasonal_growth %>% 
  rename(quarter_index = index, rgdp_growth_auto = gr) %>%
  select(quarter_index, rgdp_growth_auto)

print(this_rgdp_arima[["rgdp"]])

# pander::pander(this_rgdp_arima[["rgdp"]])

# autoplot(rgdp_uncond_fc)
# 
# knitr::kable(tail(q_rfc_growth, n = 11), digits = 1)


```

```{r all_3_uncond_arimas}

yoy3 <- 100 * make_yoy_ts(ts.union(rgdp_and_uncond_fc_auto, 
                             rgdp_and_uncond_fc_dm_nf, 
                             rgdp_and_uncond_fc_dm_f), is_log = TRUE)

# colnames(yoy3) <- c("auto", "dm_nf", "dm_f")

foo <- tail(yoy3, n = 12)

knitr::kable(foo, digits = 1)

```



## Forecasting and extending monthly data

### Implied 

